---
title: "Exploring the complexity of ecological networks using SVD entropy"
subtitle: | 
author: |
  <u>Tanya Strydom</u>, <br> 
  Gullio V. Dalla Riva & 
  Timothée Poisot
date: |
  <table style="border-style:none; padding: 0 0 50px 0; background-color:transparent" class="table"><tr>
  <th style="padding:0 30px"><a href="https://twitter.com/tanyas_08"><i class="fa fa-twitter"></i></a></th>
  </tr><tr style="background-color:transparent">
  <th style="padding:0 30px"><a href="https://twitter.com/tanyas_08"> @TanyaS_08 </a></th>
  </tr></table>
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, collapse = TRUE, comment = ">")
options(htmltools.dir.version = FALSE)
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#4B384C",
  secondary_color = "#FF961C"
)
```
# The Traditional Definition of Complexity


---

# Taking a Physical Approach to Complexity

$\mathbf{A} = \mathbf{U}\cdot\mathbf{\Sigma}\cdot\mathbf{V}^T$

$m \times m$ orthogonal matrix and
$\mathbf{V}$ an $n \times n$ orthogonal matrix. The columns in these matrices
are, respectively, the left- and right-singular vectors of $\mathbf{A}$.
$\mathbf{\Sigma}$ is a diagonal matrix, where $\sigma_{i} = \Sigma_{ii}$, which contains the singular values of $\mathbf{A}$. When the values of
$\mathbf{\sigma}$ are arranged in descending order, the singular values are
unique, though the singular vectors may not be

---

# Estimating Complexity

.pull-left[
**Using Rank Deficiency**

wkqfjqef.

$$
D = 1-\frac{r}{M}
$$
]

.pull-right[
**Using SVD Entropy**

$$
J = -\frac{1}{\ln(k)}\sum_{i=1}^k s_i\cdot\ln(s_i)
$$
]

---
# Network Structure Captures Network Complexity 

.footnote[But then things begin to tell a different story...]
---
# Complexity does not mean Robustness


---

# Structure Constrains Complexity

Annotating your code by adding comments makes it easier for you (and others) to understand what or why you decided to do what you did

---

# Although Complex, Networks Could Be Better

$$
z_i = \frac{x_i-\mu_i}{\sigma_i}
$$

---

# So What


---

class: center, middle

Presentation created using **{xaringan}**

Slides available at [https://tanyas08.github.io/Talks/2020_Dec_QCBS/](https://tanyas08.github.io/Talks/2020_Dec_QCBS/index.html#1)
